Concurrent Programming in Harmony

### 2021-11-07 book/paper.tex
Latest

\begin{figure}
\begin{code}
\harmonysource{linkedlist}
\end{code}
\caption{\harmonylink{code/linkedlist.hny} Linked list with fine-grained locking.}
\label{fig:linkedlist}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{lltest}
\end{code}
\caption{\harmonylink{code/lltest.hny} Test code for \autoref{fig:linkedlist}.}
\label{fig:lltest}
\end{figure}

@@

\autoref{fig:linkedlist} implements an ordered linked
list of integers without duplicates.
(\autoref{fig:lltest} contains test code.)
Values can be added using \texttt{insert} or deleted using \texttt{remove}.
Method \texttt{contains} checks if a particular value is in the list.

The list has two dummy ``book-end'' nodes with values \texttt{-inf} and
\texttt{inf} (similar to the Python \texttt{math.inf} constant).
An invariant of the algorithm is that at any point in time the
list is ``valid,'' starting with a \texttt{-inf} node and ending
with a \texttt{inf} node.

>>>>

\begin{figure}
\begin{code}
\harmonysource{setobj}
\end{code}
\caption{\harmonylink{code/setobj.hny} Specification of a concurrent
set object.}
\label{fig:setobj}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{linkedlist}
\end{code}
\caption{\harmonylink{code/linkedlist.hny} Implementation of a set of integers using a linked list with fine-grained locking.}
\label{fig:linkedlist}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{intsettest}
\end{code}
\caption{\harmonylink{code/intsettest.hny} Test code for \autoref{fig:linkedlist}.}
\label{fig:intsettest}
\end{figure}

@@

\autoref{fig:setobj} gives the specification of a concurrent set object.
\texttt{SetObject()} returns a pointer to a variable that
contains an empty set, rather than returning an empty set.
Values can be added using \texttt{insert()} or deleted using \texttt{remove()}.
Method \texttt{contains()} checks if a particular value is in the list.

\autoref{fig:linkedlist} implements a concurrent set of integers using
an ordered linked list of integers without duplicates.
(\autoref{fig:intsettest} contains test code.)
The list has two dummy ``book-end'' nodes with values \texttt{-inf} and
\texttt{inf} (similar to the Python \texttt{math.inf} constant).
An invariant of the algorithm is that at any point in time the
list is ``valid,'' starting with a \texttt{-inf} node and ending
with a \texttt{inf} node.
